---
output: github_document 
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 10,
  fig.height = 8
)
library(intro2jags)
```

# intro2jags

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/intro2jags/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/intro2jags/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of intro2jags is to load necessary packages and useful functions and datasets for the CMI Introduction to Coding Bayesian Models Course.

## Installation

To install the latest development version of intro2jags:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("poissonconsulting/intro2jags")
```

And to load the package into the current R session:

```{r}
# This will load several helpful packages into R.
library(intro2jags)
```

## Example Usage

### Datasets Automatically Loaded

After loading the package, the datasets can be loaded into the environment by using the `data()` function.

``` {r}
# e.g., the `penguins` dataset
data(penguins)
```

Currently, the package has 3 datasets:
  1. `penguins`
  2. `climate`
  3. `starfish`

```{r, results = "asis", echo = FALSE}
cat(licensing_md())
```
