
# intro2jags

<!-- badges: start -->
<!-- badges: end -->

The goal of intro2jags is to load necessary packages and useful functions and datasets for the CMI Introduction to Coding Bayesian Models Course.

## Installation

To install the latest development version of intro2jags:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("poissonconsulting/intro2jags")
```

And to load the package into the current R session:

```{r}
library(intro2jags)
```

## Example Usage

### Datasets Automatically Loaded

After loading the package, the datasets are available simply by calling them.

``` {r}
# e.g., the palmerpenguins `penguins` dataset
penguins
```

### Create templated analysis script

```{r, eval = FALSE}
# Call this function with the name of the analysis to create a templated 
# analysis file
# E.g., the following line of code will create a templated "abundance.R" file
# in the root directory.
analysis_template("abundance")
```


```{r, results = "asis", echo = FALSE}
cat(licensing_md())
```
